Summary of tumor cell classification with `SingleR` for `r params$library_id`

### 2024-07-22 analyses/cell-type-ewings/template_notebooks/singler-workflow/01-singler-results.Rmd
some comment updates

- Tumor cells were identified by using `AUCell`. 
These cells are labeled as `tumor_original`. 
- All other cells were labeled using `SingleR` with a combination of three references: 
  - All tumor cells annotated by `AUCell` for all other libraries in `SCPCP000015`. 
  Any cells that are labeled as tumor using this reference are labeled as `tumor_new`. 
  - `BlueprintEncodeData` from `celldex`
  - `HumanPrimaryCellAtlasData` from `celldex`

>>>>

- Tumor cells were identified by using `AUCell`. 
- All cells were labeled using `SingleR` with a combination of three references: 
  - All tumor cells annotated by `AUCell` for all other libraries in `SCPCP000015`. 
  - `BlueprintEncodeData` from `celldex`
  - `HumanPrimaryCellAtlasData` from `celldex`
